\documentclass{Standard_Resume_Format_Compact}
\setlength\columnsep{10pt}
\usepackage{color}
%\usepackage{../Templates/tfrupee}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}
\author{\textbf{VINAY SANDA}}

\Address{B V Raju Institute of Technology}

\PhoneNumber{8309516983 \hspace{6.0em}}
%\\
\Email{thevinay02@gmail.com}

\begin{document}
\maketitle
\vspace{0.1em}
\setlength{\multicolsep}{1.0em}
\colorsection{Education}
% \colorsection{Education and Scholastic Achievements}
{
\fbox{
\begin{EducationTable}
\EduDetails{B.E in Computer Science and Business System}{B V Raju Institute of Technology}{\textbf{{8.80}}}{2027}%{5/25}
\EduDetails{DIPLOMA }{Ellenki college of Engineering and Technology,Hyderabad}{\textbf{8.50} }{2024}%{10/50}
\EduDetails{X }{LEGEND HIGH SCHOOL ,Karimnagar}{\textbf{10.0}}{2021}%{4/40}
\end{EducationTable}
}
}
\vspace{1.0em}


\colorsection{Skills}
\vspace{0.5em}
\vspace{-0.8em}
\Point{Languages: C++, C, Python, Java,}
\Point{Web Technologies: HTML, CSS,Java script}
\Point{Machine Learning & AI: Deep Learning, CNNs, OpenCV, TensorFlow, PyTorch, Scikit-Learn}
\Point{Soft Skills:Problem-solving, leadership, communication, time management, adaptability, decision-making under pressure.}
\vspace{-0.0em}

\colorsection{Relevant Coursework}
\vspace{-1.0em}
\begin{multicols}{2}
\Point{Fundamentals of Computer Science}
\vspace{-0.0em}
\Point{Data Structures through C++}
\vspace{-0.0em}
\Point{Fundamentals of Economics}
\vspace{-0.0em}
\Point{Computer Organisation and Architecture}
\vspace{-0.0em}

\Point{Formal Languages and Automata Theory}
\Point{Principles of Software Engineering with UML}
\vspace{-0.0em}
\Point{Financial Management}
\vspace{-0.0em}

\Point{Operating Systems*}
\vspace{-0.0em}
\Point{DataBase Management System*
}
\vspace{-0.0em}
\Point{Object Oriented Programming through Java*}
\vspace{-0.0em}
\Point{Introduction to Innovation, IP management and Entrepreneurship*}

{\hspace{1.3em}(* - ongoing courses)}


\end{multicols}
\vspace{-0.6em}
%\end{Course}
\vspace{-0.3em}
\vspace{-0.5em}


\colorsection{Professional Experience}
 \vspace{-1.1em}
 \datedsection{\textbf{Web designing  }}{Industrial:Divine Education solutions (12th June 2023 to 30th November 2023)}
 \Point{Gained hands-on experience in Java, Python, and Web Designing.}
 \vspace{-0.1em}
\Point{Developed interactive web applications and optimized backend logic.}
% \vspace{-0.1em}
% \datedsection{\textbf{maybe one more intern}}{time}
% \Point{points again}
% \vspace{-0.3em}
% \Point{fill with filler stuff}
% \vspace{-0.3em}
%\vspace{-0.0em} 
\vspace{0.3em}

\colorsection{Projects}
\vspace{-0.4em}
\datedsection{\textbf{Remote Health Monitoring System}}{}
\Point{Built a health monitoring app for remote tracking of vitals (heart rate, temperature, BP) with real-time insights. Designed for accessibility, it enables seamless patient-professional interaction via cloud integration.}
\vspace{0.2em}

\colorsection{Hackathons and Competitions}
\vspace{-0.4em}
\datedsection{\textbf{Smart India Hackathon 2024 }}{(2024)}
\vspace{0.1em}
\Point{Developed an AI-driven agriculture marketplace app..}

\vspace{0.2em}
\datedsection{\textbf{innoWAH! 2024-25 }} {(2024-ongoing)}
\vspace{0.1em}
\Point{ Working on AI-powered health monitoring solutions.}
\datedsection{\textbf{DEMUX 2K24  }} {(2024)}
\vspace{0.1em}
\Point{  Secured 3rd place in the software category at the National Level 24-hour Hackathon.Developed remote monitoring system}





\colorsection{Leadership and Extracurriculars}
\textbf{Entrepreneurship Cell – Event Organizer} \\
Successfully organized and led \textbf{EMERGE 2025}and\textbf{PIVOT 2024}, an intercollegiate startup event that brought together innovators, industry leaders, and aspiring entrepreneurs.

\vspace{-0.1em}
\vspace{-0.0em}

\end{document}
